### 2014-10-28 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: add figures, update report

@@

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
		2 (FSW2)   	& 302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
		3 (FSW3) 	&  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
		4 (FSE4)    &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
		5 (FSE5)    &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
		6 (FSW6)    &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
		7 (FSW7)    &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
		8 (FSE8)    &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
		9 (Attic 1) &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
		10 (Attic 2)&  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
		11 (FSE1)   &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
		12 (FSW1)   &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
		13 (FSE2)   &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
		14 (FSW2)   &  Cotton w/ inner springs          &                            &  4.06 kg    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}

>>>>

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
	\caption{Delaware County, PA Fire Test Structure}
	\label{fig:DelCoSingleStory}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Fog_Instrumentation}
	\caption{Photograph of the Instrumentation in the Fog Stream Tests.}
	\label{fig:Fog_Instrumentation}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Straight_Stream_Instrumentation}
	\caption{Photograph of the Instrumentation in the Straight Stream Tests.}
	\label{fig:Straigh_Stream_Instrumentation}
\end{figure}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		2 (FSW2)   	& Water     &  30 deg Fog  	&  120 gpm    \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  &  120 gpm/60 cfm    \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  &  120 gpm    \\
		5 (FSE5)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		6 (FSW6)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		7 (FSW7)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		8 (FSE8)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		9 (Attic 1) &  Water    &  Straight Stream  &  120 gpm    \\
		10 (Attic 2)&  CAF      &  Straight Stream  &  120 gpm/60 cfm    \\
		11 (FSE1)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		12 (FSW1)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		13 (FSE2)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		14 (FSW2)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}
